---
title: "tc2899_HW2_P3"
author: "Tom"
date: "October 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


_Problem 3: Behavioral Risk Factors Surveillance System (BRFSS) for Selected Metropolitan Area Risk Trends (SMART), 2002-2010_

*Read and Clean BRFSS data*
```{r}

# importing brfss_smart2010 data

devtools::install_github("p8105/p8105.datasets") 

# add library that includes dataset 
library("p8105.datasets")
library(magrittr)

brfss_smart2010
```

```{r problem3}
# below: clean names, filter by "Overall Health", remove unwanted vars
# long -> wide with key=reponse and value= data_value
# new variable: proportion (excellent + very good / total)

brfss_data = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  select(-class, -topic, -question, 
         -sample_size, -(confidence_limit_low:geo_location)) %>% 
  spread(key = response, value = data_value) %>% 
  janitor::clean_names() %>% 
  mutate(
    prop_positive = (excellent + very_good) /
      (excellent + very_good + good + fair + poor))

brfss_data
```

#*Questions*

*How many unique locations are included in the dataset?*
*Is every state represented?* 
*What state is observed the most?*

```{r}
# unique locations: using state (locationabbr) and county (locationdesc):
nrow(distinct(brfss_data, locationabbr, locationdesc, .keep_all = FALSE))

# unique states represented:
nrow(distinct(brfss_data, locationabbr, .keep_all = FALSE))

```

```{r}

# most observed state** tbd: 

aggdata <- aggregate(brfss_smart2010, by = list(brfss_smart2010$locationabbr), 
                  FUN = sum, na.rm=TRUE)

```

*In 2002, what is the median of the “Excellent” response value?*

```{r}
# first group by year, filter to 2002 only, summarize -> median of "excellent"
group_by(brfss_data, year) %>% 
  filter(year == 2002) %>% 
  summarize(median(excellent)) 

```

*Make a histogram of “Excellent” response values in the year 2002.*

```{r}

# creating new set // first restrict by year - filter for 2002, select excellent --> hist

new_brfss = 
  brfss_smart2010 %>% 
  filter(Year == 2002) %>%
  filter(Response == "Excellent")

new_brfss

ggplot(new_brfss, aes(x = Sample_Size)) + 
  geom_histogram()

```

*Make a scatterplot showing the proportion of “Excellent” response values in New York County and Queens County (both in NY State) in each year from 2002 to 2010.*

```{r}
new_york = filter(brfss_data, locationabbr == NY)

NYC_Queens = filter(new_york, county == "New York County" | county == "Queens County")

ggplot(NYC_Queens, aes(x = year, y = Excellent, color = county)) + geom_point()
```

