---
title: "tc2899_hw2_problem1"
author: "Tom"
date: "October 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#_Problem 1: NYC Subway Transit_

#*Reading and cleaning data*

#*Directions: Read and clean the data; retain line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance. Convert the entry variable from character (YES vs NO) to a logical variable (the ifelse or recode function may be useful).*

```{r}
library(tidyverse)
getwd()
subway_data = read_csv("./NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>%
janitor::clean_names() %>%
select(-division, -exit_only, -staffing, -staff_hours, -ada_notes, -entrance_location, -entrance_longitude, -entrance_latitude, -station_location, -corner, -east_west_street, -north_south_street, -free_crossover) %>%
mutate(entry = recode(entry, "YES" = TRUE, "NO" = FALSE))
subway_data
```

#*Diretions: Write a short paragraph about this dataset – explain briefly what variables the dataset contains, describe your data cleaning steps so far, and give the dimension (rows x columns) of the resulting dataset.* 

##The previous dataset contains these variables: line, station name, station latitude/longitude, which routs is served, the new entry variable (true/false), vending (yes/no), entrance type (elevator, stair, door), and ADA compliance (true/false). 

##I ignored the undesired variables using 'select' and recoded the entry variable from character to logical using 'mutate' and 'recode'. The resulting dataset is 1,868 rows x 19 columns. 

##*Are these data tidy?*

##*How many distinct stations are there?*

##To understand how many distinct stations there are, I used the _distinct_ and _nrow()_ functions, which yielded an answer of 465 distinct stations.  

```{r}
nrow(distinct(subway_data, station_name, line))
```

##*How many stations are ADA compliant?*
```{r}
```

##*What proportion of station entrances / exits without vending allow entrance?*
```{r}
```

##*After reformatting the data so that route number and route name are distinct variables, how many distinct stations serve the A train and how many of these A trains are ADA compliant?*
```{r}
```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
